Enhance Image Classification Performance

### 2021-04-17 A-BasicCommom/CICAI2021/image_classification.tex
1.might be the last final version.

  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
  As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks.
  In this paper, by encoding image pixels using pre-trained transformers models, then connect to a fully connected layer,
  the classification model outperforms the iGPT-L model, and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
  accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.

@@

 This paper proposed a novel idea by using the pre-trained language models for image representation and take image classification
 as an example to prove its performance for Computer Vision tasks, such as image classification.
 The finding might benefit various subjects.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.

>>>>

  The \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers represents the recent popularity of many tasks in natural language processing.
  These pre-trained language models have been used to enhance computer vision tasks for many years.
  This paper uses a pre-trained transformer model to encode image pixels, and then connects to the fully connection layer, dropout layer and Softmax layer.
  The performance of the classification model is better than the current best iGPT-L model.
  It surpasses the current best accuracy in the CIFAR-10/100 image set and the COVID-19 tomographic image classification set.

@@

This article proposes a new idea of using pre-trained language models for image characterization and image classification.
Through empirical analysis, the negative impact of the transformer on the CNN model is discussed, and it is proved that the pre-trained language model can improve the performance in image classification.
This finding may benefit various topics of computer vision tasks.
The test shows that the proposed model is better than the classification effect of the iGPT-L model without enhancing the image data set.
The accuracy is $99.60\%\sim99.74\%$ on the CIFAR-10 image set, $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and $99.51\%\sim100.00\%$ on the COVID-19 tomographic image test set.
